% Write your acknowledgements here

%
This work was supported by the SPRING program of the Japan Science and Technology Agency (JST SPRING, Grant Number JPMJSP2139), and MM Bridge CO., LTD.

I would like to express my sincere gratitude to my supervisor Professor Takashi Yamaguchi for his support and professional guidance. And he has been a patient advisor to me not only in my research, but also in my life during my study abroad.

Many thanks to lab staff secretary Machiko Kitami provide a good work environment, to Assistant Professor Gen Hayashi provide me advice, and to Ryo Sakura who is the people in the same grade help for his help and support in Japanese language and research. Also thanks to MM Bridge Co. Ltd. Motoshi Yamauchi, Keita Ueno provides me important advice and construction data, and Nippon Steel Bolten Co. Masayori Yoshimi provide me advice and bolt. Also thanks the members of OCU Machining Technology Centre, especially Tatumi Suga, for their assistance in making test pieces and providing suggestions for production.

I had also like to thank my tutor Lang Yu, who is also an international student, for his guidance and support, and Lai Jianpeng for helping me with my life.

To my former and present colleagues, Kensuke Toda, Shun Matsui, Li Ruoxi, Misato Konishi: thank you for your support and language lessons. I also would like to thank all the former or present members of the research lab who helped my experiments.

I had the pleasure of visiting Delft University of Technology in the Netherlands. Therefore, I would like to thank Professor Milan Veljkovic for inviting me and for patiently guiding me, as well as Dr. Iman Shakeri and David Malschaert for their support.

I would like to express my deepest gratitude to my ex-girlfriend Cui Yi for providing me with great support in life as well as mental and to be by my side during my studies abroad, enabling me to focus on my research.

I would also like to grateful my parents and sister for caring and supporting me during my study abroad. Also very thanks my cats Kanna and Banana, my friend Xia Yu (Hinamizawa) for accompanying me through a tough time helped me mentally.

\null\hfill Chen Yu (陳瑜) \\
\null\hfill Osaka, Japan, Jan 2024